---
title: "cd_biz"
author: "Brook Frye"
date: "9/4/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("~/utils/00_load_dependencies.R")
source("code/biz_dsny_complaints_2023.R")

# use bizdt bizshp for the merged business/complaint data
```

#### Map of DSNY complaints related to businesses from 2022 - present. Includes the following complaint types for streets and sidewalks:
- Commercial Disposal Complaint 
- Retailer Complaint
- Dirty Condition

*** 

##### We are sourcing business data from:
- [Vacant storefront registration](https://data.cityofnewyork.us/City-Government/Storefronts-Reported-Vacant-or-Not/92iy-9c3n)
- [DCA licenses](https://nycopendata.socrata.com/Business/Legally-Operating-Businesses/w7w3-xahh/data)
- [Restaurants]
- [Supermarkets]

```{r}

int_cd_biz <-
  classInt::classIntervals(cd_biz$n_cmpts_p_biz, n = 6)

pal_biz = leaflet::colorBin(
  # issues with councildown's colorBin
  palette = c("#b3b3ff","#1850b5","#1f3a70","#ba9f64","#af6d46","#660000"),
  bins = int_cd_biz$brks,
  domain = round(cd_biz$n_cmpts_p_biz, 2),
  na.color = "White",
  reverse = FALSE
)

m_biz <- leaflet() %>% 
  addCouncilStyle(add_dists = TRUE) %>% 
  leaflet::addPolygons(data=cd_biz, 
                       fillColor = ~pal_biz(n_cmpts_p_biz), 
                       label = ~paste0(n_cmpts_p_biz), 
                       opacity = 0) %>% 
  addLegend(pal = pal_biz, 
            values = int_cd_biz$brks, 
            position = "topleft", 
            title = "Complaints per Business by <br/> Council District")


mapview::mapshot(m_biz, "visuals/dsny_biz_cmplts_2022-sept2023.html")
```

##### Litter basket inventory
- overflowing litter basket complaints
- worst litter baskets

```{r}

library(nngeo)

# get litter basket locations, buffer and create polygon
lburl <- "https://data.cityofnewyork.us/api/geospatial/8znf-7b2c?accessType=DOWNLOAD&method=export&format=Shapefile"
lbz <- unzip_sf(lburl)
lb_points_buf <- st_read(lbz) %>%
  st_buffer(dist = 10) %>% 
  st_cast("MULTIPOLYGON")

# litterbasket complaints points, make sf
lbc_points <- ds_litter_sub %>% 
  st_as_sf(wkt = "location", crs = 4326) %>% 
  st_transform('+proj=longlat +datum=WGS84') 

lb_points_buf <- lb_points_buf %>% st_transform('+proj=longlat +datum=WGS84')


fsub <- st_filter(lb_points_buf, lbc_points)
fsub %>% group_by(geometry) %>% 
  summarise(n=length(unique(basketid)))



# lcnn <- st_nn(lb_points, lbc_points, k=1000, maxdist = 10, returnDist = TRUE)
# test <- data.table(id = c(1:length(lcnn$nn)), distnc = lcnn$dist, comps = lengths(lcnn$nn)>0)
# test[comps==TRUE, ]

leaflet() %>% 
  addCouncilStyle(add_dists = TRUE) %>% 
  leaflet::addCircleMarkers(data = f_sub, 
                      opacity = .5, 
                      radius = .0,
                      weight = .05) %>% 
  leaflet::addCircles(data = lbc_points, 
                      color = "Black")
                      
                      , 
                      radius = .005)


```


#### Scorecard - Street Cleanliness

- by DSNY sections via 

```{r}
url <- "https://data.cityofnewyork.us/api/geospatial/7vgu-qbur?accessType=DOWNLOAD&method=export&format=Shapefile"
file <- unzip_sf(url)
ds_sects <- st_read(file)

sc <- fread("https://data.cityofnewyork.us/api/views/rqhp-hivt/rows.csv?accessType=DOWNLOAD")
# sc[, cleaning_section := as.character(cleaning_section)]
sc$year <- unlist(lapply(strsplit(sc$Month, " ", fixed = TRUE), "[[", 1))
sc$month <- unlist(lapply(strsplit(sc$Month, " ", fixed = TRUE), "[[", 3))

sc_sub <- sc[year %in% "2023" & month %in% "07", ]

sc_sf <- ds_sects %>% 
  left_join(sc_sub, by = c("section" = "Cleaning Section")) %>% 
  st_as_sf() %>% 
  st_transform('+proj=longlat +datum=WGS84')
```


```{r}
# map dirty zones 
pal <- leaflet::colorNumeric(palette = c("#b3b3ff","#1850b5","#1f3a70","#ba9f64","#af6d46","#660000"), 
                         domain = sc_sf$`Acceptable Sidewalks %`, 
                         na.color = "White")

unique(pal(sc_sf$`Acceptable Sidewalks %`))

dirty_sects <- leaflet() %>% 
  addCouncilStyle(add_dists = TRUE) %>% 
  leaflet::addPolygons(data=sc_sf, 
                       color = ~pal(`Acceptable Sidewalks %`), 
                       fillColor = ~pal(`Acceptable Sidewalks %`), 
                       label = ~paste0(`Acceptable Sidewalks %`), 
                       opacity = 0, 
                       fillOpacity = .2) #%>% 
  addLegend(pal = pal, 
            values = sc_sf$`Acceptable Streets %`, 
            position = "topleft", 
            title = "Complaints per Business by <br/> Council District")

```


```{r}

# commercial waste zones

cd_biz <- leaflet(biz_shps) %>% 
  addProviderTiles("CartoDB") %>% 
  addPolygons(weight = .5,
              fillColor = ~pal(nbiz), 
              popup = paste(biz_shps$nbiz, biz_shps$boro_cd), 
              stroke = TRUE, 
              fillOpacity = .9) %>% 
  addLegend(pal = pal, 
            values = biz_shps$nbiz) 
```

