---
title: "SanitationRQ_8.23.23"
output: html_document
date: "2023-08-23"
---

Good morning! Here's the 311 data you asked for on street cleanliness (DSNY), illegal dumping (DSNY), derelict vehicles (DSNY), and catch basin complaints (DEP). For catch basin complaints, this includes complaints located at catch basins as well complaints that had 'catch basin' in the complaint description. 

For grease (DEP) - I couldn't find anything specifically on yellow and brown grease, but I've attached the complaints that contained the word 'grease' in the description. 

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(vroom)
library(leaflet)
library(leaflet.extras)
library(janitor)
library(data.table)
library(zoo)
library(councildown)
```

- 311 Data on Street Cleanliness Complaints Over Time and by Community District (We used similar data on in March 2022 hearing) 

- 311 Data on Illegal Dumping 

- 311 Data on Derelict Vehicles 

- 311 Data on Catch Basin Complaints Over Time and by Community District 
  subset to complaints located at catch basins, contains catch basin in the description of complaint

- Any data available on the disposal of yellow and brown grease 

**Using 311 complaints available from 2018 and beyond:**

```{r}
# dsny_311 <- fread("https://data.cityofnewyork.us/resource/fhrw-4uyv.csv?agency='DSNY'&$where=created_date>='2018-01-01'&$limit=999999999999")
dsny_311 <- fread("https://data.cityofnewyork.us/resource/fhrw-4uyv.csv?agency='DSNY'&$where=created_date>='2022-08-01'&$limit=999999999999")
```

```{r}
setDT(dsny_311)
dsny_311[, created_date := as.Date(created_date)][, yr := year(created_date)][, mo := month(created_date)]
dsny_311[, date_ym:=as.yearmon(created_date)]
```

```{r}
dsny_311 <- dsny_311 %>% filter(created_date >= "2022-08-01" & created_date < "2023-09-01")
```



#### STREET CLEANLINESS ####

Using Brook's code from Feb 23.

```{r}
od_dl <- dsny_311
```

```{r}
# let's group in a sensible way to reduce categories
od_dl[complaint_type %in% "Missed Collection (All Materials)", complaint_type := "Missed Collection"]

od_dl[grepl("Litter", complaint_type) | grepl("litter", complaint_type), complaint_type := "Litter"]

od_dl[complaint_type %in% c("Overflowing Litter Baskets", "Dirty Condition", "Dirty"), complaint_type := "Dirty Conditions"]
# change, take out littering and make own chart

od_dl_sub <- od_dl[complaint_type %in% c("Dirty Conditions", "Missed Collection", "Litter")]
```

```{r}
sani_yrs_sub <- od_dl_sub[, .N, by = yr][order(yr, decreasing = TRUE
)]

# total number of DSNY complaints
od_dl_yrs <- od_dl[, .N, by = yr]
setnames(od_dl_yrs, "N", "Total DSNY")
setnames(sani_yrs_sub, "N", "Dirty/Missed Collection")
yrs_dsny <- merge(od_dl_yrs, sani_yrs_sub)
od_dl_sub[, n_comp := .N, by = c("complaint_type", "date_ym")]
od_dl_sub <- od_dl_sub[, .(complaint_type, date_ym, n_comp)]
od_dl_sub <- unique(od_dl_sub)
# od_dl_sub[complaint_type %in% "Missed Collections" & ]
```

```{r}
# ---- Street cleanliness over time: plot
ggplot(od_dl_sub[od_dl_sub$date_ym < "2023-09-01"], aes(x= date_ym, y=n_comp, color=complaint_type), group=complaint_type) + geom_line() + 
  theme_bw() + labs(x="Date", y="Number of Complaints", title="311 Data on Street Cleanliness Complaints Over Time", 
                    subtitle="Jan 2018 - July 2023", colour="Complaint type") + theme_nycc()
ggsave(filename = "clean_over_time.png", path = "visuals", width=10, height=7)
# ---- Street cleanliness over time: plot
ggplot(od_dl_sub[od_dl_sub$date_ym < "2023-09-01"], aes(x= date_ym, y=n_comp, color=complaint_type), group=complaint_type) + geom_smooth(method="loess", se=FALSE) + 
  theme_bw() + labs(x="Date", y="Number of Complaints", title="311 Data on Street Cleanliness Complaints Over Time", 
                    subtitle="Jan 2018 - July 2023", colour="Complaint type") + theme_nycc() # + scale_color_discrete(palette="diverging")
ggsave(filename = "clean_over_time_smooth.png", path = "visuals", width=10, height=7)
```

```{r}
# ---- Street cleanliness over time: table
# od_dl_sub[od_dl_sub$date_ym < "2023-09-01"] %>% arrange(complaint_type)
clean_over_time_df <- dcast(melt(as.data.table(od_dl_sub[od_dl_sub$date_ym < "2023-09-01"]), id.vars = c("complaint_type", "date_ym")), 
      date_ym + variable ~ complaint_type, value.var = "value") %>% select(date_ym, `Dirty Conditions`, `Missed Collection`, `Sanitation Condition`)
# clean_over_time_df
write.csv(clean_over_time_df, "data/output/clean_over_time.csv")
```

```{r}
# ---- Street cleanliness by community district: table
clean_by_cd_df <- od_dl[complaint_type %in% c("Dirty Conditions", "Missed Collection", "Sanitation Condition")] %>% group_by(community_board) %>% summarise(count=n())
# clean_by_cd_df
write.csv(clean_by_cd_df, "data/output/clean_by_comm.csv")
```

#### ILLEGAL DUMPING ####

```{r}
# subset DSNY complaints to illegal dumping
dsny_311_id <- dsny_311[dsny_311$complaint_type == "Illegal Dumping",]
# unique(dsny_311_id$complaint_type)
```

```{r}
# ---- Illegal dumping over time: table
id_over_time_df <- dsny_311_id %>% group_by(date_ym) %>% summarise(n_comp=n())
id_over_time_df
write.csv(id_over_time_df, "data/output/id_over_time.csv")
# dsny_311_id_my
```

```{r}
# ---- Illegal dumping over time: plot
ggplot(id_over_time_df[id_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_smooth(method="loess", se=FALSE) + labs(x="Date", y="Number of Complaints", title="311 Data on Illegal Dumping Complaints Over Time", subtitle="Sep 2021 - July 2023 \nData includes complaints filed with DSNY, excludes DEP.") + theme_nycc() 
ggsave(filename = "id_over_time_smooth.png", path = "visuals", width=10, height=7)
ggplot(id_over_time_df[id_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_line() + labs(x="Date", y="Number of Complaints", title="311 Data on Illegal Dumping Complaints Over Time", subtitle="Sep 2021 - July 2023 \nData includes complaints filed with DSNY, excludes DEP.") + theme_nycc() 
ggsave(filename = "id_over_time.png", path = "visuals", width=10, height=7)
```

```{r}
# ---- Illegal dumping by community district: table
id_by_cd_df <- dsny_311_id %>% group_by(community_board) %>% summarise(n_comp=n())
id_by_cd_df
write.csv(id_by_cd_df, "data/output/id_by_comm.csv")
```

#### DERELICT VEHICLES ####

```{r}
# subset DSNY complaints to derelict vehicles
dsny_311_dv <- dsny_311[dsny_311$complaint_type == "Derelict Vehicles",]
```

```{r}
# ---- Derelict vehicles over time: table
dv_over_time_df <- dsny_311_dv %>% group_by(date_ym) %>% summarise(n_comp=n())
dv_over_time_df
write.csv(dv_over_time_df, "data/output/dv_over_time.csv")
```

```{r}
# ---- Derelict vehicles over time: table
ggplot(dv_over_time_df[dv_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_smooth(method="loess", se=FALSE) + labs(x="Date", y="Number of Complaints", title="311 Data on Derelict Vehicle Complaints Over Time", subtitle="Jan 2018 - July 2023") + theme_nycc() 
ggsave(filename = "dv_over_time_smooth.png", path = "visuals", width=10, height=7)
ggplot(dv_over_time_df[dv_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_line() + labs(x="Date", y="Number of Complaints", title="311 Data on Derelict Vehicle Complaints Over Time", subtitle="Jan 2018 - July 2023") + theme_nycc() 
ggsave(filename = "dv_over_time.png", path = "visuals", width=10, height=7)
```

```{r}
# ---- Derelict vehicles by community district: table
dv_by_cd_df <- dsny_311_dv %>% group_by(community_board) %>% summarise(n_comp=n())
write.csv(dv_over_time_df, "data/output/dv_by_comm.csv")
```

-------------------

```{r}
dep_311 <- fread("https://data.cityofnewyork.us/resource/fhrw-4uyv.csv?agency='DEP'&$where=created_date>='2018-01-01'&$limit=999999999999")
```

```{r}
setDT(dep_311)
dep_311[, created_date := as.Date(created_date)][, yr := year(created_date)][, mo := month(created_date)]
dep_311[, date_ym:=as.yearmon(created_date)]
```

#### CATCH BASIN COMPLAINTS ####

```{r}
# subset to complaints located at catch basins, contains catch basin in the description of complaint
dep_311_cb <- dep_311[grepl("catch", dep_311$location_type, ignore.case = TRUE) | grepl("catch", dep_311$descriptor, ignore.case = TRUE),]
dep_311_cb
```

```{r}
# ---- Catch basin over time: table
cb_over_time_df <- dep_311_cb %>% group_by(date_ym) %>% summarise(n_comp=n())
cb_over_time_df
write.csv(cb_over_time_df, "data/output/cb_over_time.csv")
```

```{r}
# ---- Catch basin over time: plot
ggplot(cb_over_time_df[cb_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_smooth(method="loess", se=FALSE) + labs(x="Date", y="Number of Complaints", title="311 Data on Catch Basin Complaints Over Time", subtitle="Jan 2018 - July 2023 \nData includes complaints located at catch basins or containing 'catch basin' in desc.") + theme_nycc()
ggsave(filename = "cb_over_time_smooth.png", path = "visuals", width=10, height=7)
ggplot(cb_over_time_df[cb_over_time_df$date_ym < "2023-09-01",], aes(x= date_ym, y=n_comp)) + geom_line() + labs(x="Date", y="Number of Complaints", title="311 Data on Catch Basin Complaints Over Time", subtitle="Jan 2018 - July 2023 \nData includes complaints located at catch basins or containing 'catch basin' in desc.") + theme_nycc() 
ggsave(filename = "cb_over_time.png", path = "visuals", width=10, height=7)
```

```{r}
# ---- Catch basin by community district: table
cb_by_cd_df <- dep_311_cb %>% group_by(community_board) %>% summarise(n_comp=n())
write.csv(cb_by_cd_df, "data/output/cb_by_comm.csv")
```

#### YELLOW AND BROWN GREASE ####

```{r}
dep_311_grease <- dep_311[grepl("grease", dep_311$descriptor, ignore.case = TRUE),]
dep_311_grease
write.csv(dep_311_grease, "data/output/all_grease_data.csv")
```





